# Dissertation Abstracts {-}

In this section you will find all the dissertation abstracts submitted, arranged by Surname.

```{r abstracts-general, echo=FALSE, warning=FALSE, message=FALSE}

library(tidyverse)

abstracts_count <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  group_by(initial) %>%
  count()

```

## Surnames beginning with A {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "A")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with B {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "B")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with C {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "C")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with D {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "D")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with F {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "F")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with G {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "G")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with H {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "H")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with J {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "J")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with K {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "K")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with L {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "L")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with M {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "M")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with N {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "N")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with O {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "O")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with P {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "P")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with R {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "R")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with S {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "S")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with T {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "T")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with V {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "V")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```

## Surnames beginning with W {-}

```{r, echo=FALSE, message=FALSE, results='asis'}

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "W")

for(i in 1:dim(abstracts)[1]){
  cat("**Name: **", abstracts$StudentName[i], "\n\n")
  cat("**Supervisor: **", abstracts$Supervisor[i], "\n\n")
  cat("**Title: **", abstracts$Titles[i], "\n\n")
  cat("**Abstract: **", abstracts$Abstract[i], "\n\n")
  cat("---\n\n")
}
```